\thetitle

### 2021-03-03 writing/sample.tex
sample: rewording

As is, the chosen mutators generate a huge number of debugging scenarios,
approximately 1,000,000 for the chosen benchmark. This number of scenarios is
far too large to even identify the interesting ones among them.  Furthermore
this population is heterogeneous; different scenarios come from different
mutants and different mutants are the result of a different mutator and
benchmark pair.

To make the experiment computationally feasible and statistically sound,
stratified uniform random sampling with three levels of stratification becomes
necessary.  The first two levels group mutants first by benchmark and then by
mutator.  The set of the randomly selected mutants of each benchmark is
checked to make sure that, per benchmark, the sample reflects the diversity of
mutants with respect to the mutators that generated them.  Specifically, the
process samples 80 mutants with interesting scenarios per benchmark,
evenly-distributed across all of the mutators that contribute mutants for the
benchmark. Some benchmarks has less than  80 mutants with interesting scenarios
in which case the process collects them all which results in a total of 756 mutants
across all benchmarks.  
At the third level, the sampling process draws 96 random interesting
scenarios from each configuration lattice with replacement. In sum, the
final sample consists of 72,200 interesting scenarios.

>>>>

As is, the chosen mutators generate a huge number of debugging scenarios:
approximately 1 million for the chosen benchmarks. This number of scenarios is
far too large to even identify the interesting ones among them.  Furthermore
this population is heterogeneous; scenarios come from different
mutants, and the mutants are the result of different mutators applied to each
benchmark.

To become computationally feasible and statistically sound, the experiment employs
stratified uniform random sampling with three levels of stratification.
The first two levels group mutants first by benchmark and then by
mutator, making sure that the sample within each benchmark reflects the diversity of
mutants with respect to the mutators that generated them.  Specifically, the
experiment samples 80 interesting mutants per benchmark,
evenly-distributed across all of the mutators that contribute mutants for the
benchmark. Some benchmarks have less than  80 mutants with interesting scenarios,
in which case the only choice is to take them all.
The result is a total of 756 interesting mutants across all benchmarks.
Finally, the third level of sampling draws 96 random interesting debugging
scenarios from each configuration lattice with replacement. The
final sample thus consists of 72,192 interesting scenarios.
